6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
Repeated word

As well as the monitoring of live systems, I have also discovered a number of other unintended use cases for the tool, a popular idea is to run the test suites on a continuous integration server to verify to verify the correctness of configuration management recipes. A machine could be prepared with the configuration management tool, and a suite of tests used to verify its validity.

>>>>

As well as the monitoring of live systems, I have also discovered a number of other unintended use cases for the tool, a popular idea is to run the test suites on a continuous integration server to verify the correctness of configuration management recipes. A machine could be prepared with the configuration management tool, and a suite of tests used to verify its validity.
